EEG2fMRI: Cross-Modal Synthesis for Functional Neuroimaging

### 2021-05-03 article/article.tex
Update

\begin{abstract}
    Functional neuroimaging techniques are essential in advancing research in neuroscience. However, existing techniques require researchers to either compromise on spatial resolution, temporal resolution, cost, or portability. We attempt to model the  mapping between concurrent EEG and fMRI recordings using various machine learning architectures, in order to combine the complementary qualities of the two modalities. Although initial results in a within-subject regime are promising, the limited quantity of multi-modal recordings currently available appears to be a major obstacle in generalizing to new subjects.
\end{abstract}

@@

Neural activity is central to investigating cognition. In cognitive neuroscience, it has been employed to study the neural correlates of many cognitive functions, such as perception, attention, and memory. In cognitive modelling, neural activity has been used to inform the development of a wide range of cognitive architectures. In clinical neuroscience, it has been employed for investigating, diagnosing, and ameliorating a wide range of neurological conditions.

@@

>>>>

\begin{abstract}
    Functional neuroimaging techniques are essential in advancing research in neuroscience. However, existing techniques require researchers to either compromise on spatial resolution, temporal resolution, cost, or portability. We attempt to model the  mapping between concurrent EEG and fMRI recordings using various machine learning architectures, in order to combine the complementary qualities of the two modalities. The trained model is then able to reconstruct fMRI data from simultaneous EEG data. Although initial results in a within-subject regime are promising, the limited quantity of multi-modal recordings currently available appears to be a major obstacle in generalizing to new subjects.
\end{abstract}

@@

Neural activity is central to investigating cognition. In cognitive neuroscience, it has been employed to study the neural correlates of many cognitive functions, such as perception, attention, and memory. In cognitive modelling, neural activity has been used to inform the development of a wide range of cognitive architectures. In clinical neuroscience, it has been employed for investigating, diagnosing, and ameliorating a wide range of neurological conditions \cite{n_functional_2015}.

@@

\bibliographystyle{plain}
\bibliography{eeg2fmri}
